COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries

### 2021-07-17 2_tables.Rmd
clean up
1_cleaning.Rmd preserved but not called
3_main_text.Rmd called rather than call to googledrive
removal of legacy files

---
title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    code_folding: hide
    toc: yes
    toc_float: yes
    self_contained: yes
  bookdown::html_document2: default
keywords: vaccine hesitancy
---

>>>>

---
title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code'
date: "1 July 2021"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    code_folding: hide
    toc: yes
    toc_float: yes
    self_contained: yes
  bookdown::html_document2: default
keywords: vaccine hesitancy
---

### 2021-07-17 3_main_text.Rmd
clean up
1_cleaning.Rmd preserved but not called
3_main_text.Rmd called rather than call to googledrive
removal of legacy files

<!-- KEEP ALL REVISIONS IN SUGGESTING MODE FOR VERSION CONTROL - DO NOT ACCEPT CHANGES -->
<!-- COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging -->

>>>>

<!-- COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging -->

### 2021-07-17 paper.Rmd
clean up
1_cleaning.Rmd preserved but not called
3_main_text.Rmd called rather than call to googledrive
removal of legacy files

---
title: "COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries"
output: 
  bookdown::pdf_document2:
    keep_tex: true
    latex_engine: xelatex
    pandoc_args:
      - --template=4_paper_supplementary_files/mytemplate.latex
    toc: false
    extra_dependencies:
      caption: ["font={bf,normalsize}"]
      mathptmx: null
  bookdown::word_document2: default
bibliography: 4_paper_supplementary_files/bib_final.bib
csl: 4_paper_supplementary_files/nature.csl
header-includes:
  - \setmainfont{Arial}
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage{titlesec}
  - \usepackage{hyperref}
  - \titleformat*{\subsection}{\normalsize\bfseries}
  - \titleformat*{\section}{\large\bfseries}
  - \usepackage{float} \floatplacement{figure}{H} 
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
# linestretch: 1.5
urlcolor: blue
link-citations: yes
linkcolor: blue
fontsize: 12pt
---

@@

```{r load_gdoc, include = FALSE, eval = TRUE}

googledrive::drive_download(file = "NatureMedicine Covid vaccine hesitancy FINAL", 
                            path = "4_paper_supplementary_files/Intro Vaccine.txt", overwrite = TRUE)

file.rename(from = "4_paper_supplementary_files/Intro Vaccine.txt", 
            to = "4_paper_supplementary_files/temp_download.Rmd")

@@

```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}

>>>>

---
title: "COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries"
output: 
  bookdown::pdf_document2:
    keep_tex: true
    latex_engine: xelatex
    pandoc_args:
      - --template=4_files/mytemplate.latex
    toc: false
    extra_dependencies:
      caption: ["font={bf,normalsize}"]
      mathptmx: null
  bookdown::word_document2: default
bibliography: 4_files/bib_final.bib
csl: 4_files/nature.csl
header-includes:
  - \setmainfont{Arial}
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage{titlesec}
  - \usepackage{hyperref}
  - \titleformat*{\subsection}{\normalsize\bfseries}
  - \titleformat*{\section}{\large\bfseries}
  - \usepackage{float} \floatplacement{figure}{H} 
  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
# linestretch: 1.5
urlcolor: blue
link-citations: yes
linkcolor: blue
fontsize: 12pt
---

@@

@@

```{r main_text, child = "3_main_text.Rmd"}
